---
title: "R&MaxEnt seminer in Kazakh"
output: html_document
# toc: TRUE
---
<!-- Self Introduction -->
<!-- - PhD student at RakunoGakuenUniv. -->
<!-- - Landscape Ecology using GIS,RS -->
<!-- - Data analysis with R -->
Widows User Name 

#todo
toc
page

##Install Software

install these software newest version.  
- R 3.40  
- Rstudio 1.0.143  
- MaxEnt *depends  
Using R with Rstudio is most powerful for data analysis!

##First Step in R language (classical R)
###object?
called as 'object', what stroes 'variable' and 'function' in R  
R codes shows in this box. plz type in console
```{r}
100 * 100 - 100 / 100
test <- 100
test * 10
```

###assign/insert object
->, <-, =, assign()  
below codes means same!
```{r}
test2 <- 100
test3 = 100
100 -> test4
assign("test5",100)
c(test2,test3,test4,test5)
```

###data type
```{r}
num <- 100
class(num)
cha <- "string or charactor"
class(cha)

true_b <- TRUE
false_b <- FALSE
class(true_b)

(fcr <- as.factor(c("A","B","C")))
class(fcr)
```

###data structure
```{r}
#vector
v <- c(1,2,3,4)
v

#must be same type
v2 <- c("1","2",3,TRUE)
v2

#matrix
mx <- matrix(c(1:16),nrow = 4)
mx

#list can contain all type
l <- list(c(1,2),"3",TRUE)
l

#dataframe is made from multiple vectors which have same length
dat <- data.frame(c(1,2,3,4),letters = c("A","B","C","D"))
dat
```


function
```{r}
(seq(1,10) -> a) # assign and print
head(a) # print 1:6 from head
tail(a) # print 1:6 from tail
```



```{r}

```















